SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
messing about with arrows
some minor typos (all the important stuff)

We will start by looking at the visual foraging data from Clarke et al (2022), QJEP. As the current version of our model only takes the $p_A$ bias into account for the initial taret selection, we will ignore these data points for now.

@@

```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model. (*right*) The proportion of trials the item with the largest assigned weight as selected by the participant.  Each dot shows data from an individual particpant in a condition and the shaded region indicates the invertal in which we expect 67% of participants to fall."}

@@

We can also repeat this calculate for all other items during/in a trial - is our model accurate/calibrated in cases when 
the participant did not select the item withe highest model weight?

@@

plts[[1]] + plts[[2]] 
```

>>>>

We will start by looking at the visual foraging data from Clarke et al (2022), QJEP. As the current version of our model only takes the $p_A$ bias into account for the initial target selection, we will ignore these data points for now.

@@

```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model. (*right*) The proportion of trials the item with the largest assigned weight as selected by the participant.  Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}

@@

We can also repeat this calculate for all other items during/in a trial - is our model accurate/calibrated in cases when 
the participant did not select the item with the highest model weight?

@@

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8"))
```
